---
title: "Codebook"
output: html_document
---
```{r}

df <- read.csv("tidydata.txt", sep=" ")
tidydata <- read.csv("averaged_tidydata.txt", sep=" ")
```

# Provided dataset 

The data for the project can be found here:

https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip


It is also in this course repository. Information on the original features and the experiments to collect the data can be found in the features_info.txt and README.txt.   

Any changes to the varibale names to the data are highlighted below.  


#Datasets produced
##Tidy Dataset (tidydata.txt)
The tidy data contains a total of `r length(df)` columns in this data set. Each row contains data related to an activity for a unique person. There are `r length(unique(df$activityName))` distinct activities: 

```{r}
levels(df$activityName)
```

As well as `r length(unique(df$subject))`unique subjects (people). 


##Averaged Tidy Dataset (averaged_tidydata.txt)

The Averaged tidy data set contains the average value for each variable per person and action. Therefore this dataset has `r nrow(tidydata)` rows. 



#Variable Names

subject - Number between 1 and 30 representing the person.  
activityName - Given name of activity. One of the six described above.  

Some variable names were changed from the original dataset for readability:    
  
*  Variables starting with f have been changed to freq and those starting with t to time. These represented the "FrequencyDomain" and "TimeDomain" depending on of the data was before or after the Fast Fourier Transform.    
*  Brackets and dashes were removed from the original variable names as well.   

The variable names have several parts:  
  
*    First part represents the Domain either time or frequency.   
*    The instrument is given by Acc or Gyro to represent accelerometer or gyroscope data.  
*    The acceleration measured BodyAcc or GravityAcc.  
*    Other specific movement data is stored with Jerk or Mag (Magnitude) in the variable name.  
*    Mean and std stand for the mean or standard deviation of the data.   
*    The axis of the motion is represented by X, Y or Z.  

This resulted in the following 68 column names: 
```{r}
names(df)
```
